Multi-scale assessment of a grassland productivity model

### 2020-12-27 manuscript/manuscript.Rmd
add mean cvmae equation

>>>>

Parameterization was done using differential evolution, a global optimization algorithm, to minimize the mean coefficient of variation of the mean absolute error (\textit{F}, Eq. 1), which accounts for variation among sites [@choler2011].

\begin{equation}
F = \frac{1}{N}\sum_{j=1}^{N}CVMAE_{j}
\end{equation}

\begin{equation}
CVMAE_{j} = \frac{\frac{1}{i}\sum_{i=1}^{n}|fCover_{i,obs} - fCover_{i,pred}|}{\overline{fCover_{obs}}}
\end{equation}

where \textit{N} is the number of sites and \textit{n} is the number of daily values at each site, \textit{fCover\textsubscript{i,obs}} and \textit{fCover\textsubscript{i,pred}} are observed and predicted values, respectively. \textit{fCover\textsubscript{pred}} is the average observed \textit{fCover} at each site.
